\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards \vspace{-2ex} \versionline{14}

### 2016-02-05 ICRA2016/bandits_docs/includes/dataset.tex
Made first round of ICRA revisions, v14 of the paper

\subsection{Grasp Sampling}
\seclabel{grasp-sampling}
Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and their $P_F$.
We generate $N_g$ grasps for each object using a modification of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
Let $w$ be the maximal opening of the gripper, $\hat{\gamma}$ be a sampled friction coefficient, and $\mS$ be the set of points on the object surface for an SDF $f$ as described in \secref{grasp-param}.
To sample a single grasp, we first generate a contact point $\bc_1$ by sampling uniformly from $\mS$.
Next we sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone and compute $\bc_2 = \bc_1 + (w - t_2^*) \bv$ and $\bx = 0.5 (\bc_1 + \bc_2)$, where $t_2^*$ is defined as in \secref{contact}.
This yields a grasp $\bg_{i,k} = (\bx, \bv)$.
We add $\bg_{i,k}$ to the candidate set if the contacts are antipodal~\cite{mahler2015gp}, or $\bv^T \bn_1 \leq \cos(\arctan(\hat{\gamma}))$ and $\bv^T \bn_2 \leq \cos(\arctan(\hat{\gamma}))$.

We evaluate $P_F(\bg)$ using Monte-Carlo integration~\cite{kehoe2012toward} by sampling the object pose, gripper pose, and friction random variables $N_s$ times and recording $S_{i,k}$, the number of samples for which grasp $\bg_{i,k}$ was in force closure.
The dataset of $N_o$ objects and $N_g$ candidate grasps per object is $\mD = \{ (S_{i, k}, \mY_{i, k}) \big| i = \{1, ..., N_o\}, k = \{1, ..., N_g\} \}$ where $\mY_{i,k} = (\bg_{i, k}, \mO_i) \in \mM$ is a grasp-object pair in Dex-Net.

@@

\subsection{Grasp Differential Heightmap Features}
\seclabel{grasp-similarity}
To measure grasp similarity, we embed each grasp $\bg = (\bx ,\bv)$ on object $\mO$ in Dex-Net in a feature space based on 2D projections of the local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
Let $\delta \in \mathbb{R}$ be the pixel resolution in meters, and let $r \in \mathbb{R}$ be a minimum projection distance.
%Furthermore, let $\bc_i, i = 1, 2$ be a contact point for grasp $\bg$ and let $\bt_1, \bt_2$ be two orthogonal unit vectors to the grasp approach direction $\bv$.
The heightmap $\bh_{i}$ at contact $\bc_i$ maps points $\bp \in \bR^3$ on the tangent plane $\bv^T(\bp - \bc_1) = 0$ to the distance to the surface along $\bv$.
To compute the value at pixel $u,v$, we compute the location of the pixel on the plane $\bp_i(u,v) = \bc_i + \delta u \bt_1 + \delta v \bt_2$ and assign
\begin{align*}
	\bh_i(u,v) = \minimum{t \geq -r} t \text{ such that } f\left( \bp_i(u,v) + (-1)^{i} t \bv \right) = 0
\end{align*}
\noindent where $f$ is the SDF of object $\mO$. 
We make $\bh_i$ rotation-invariant by orienting its axes to align with the eigenvectors of the weighted covariance matrix of the 3D surface points that generate the heightmap as described in~\cite{salti2014shot}.
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
Since force closure depends on object surface normals at contacts~\cite{pokorny2013c}, we finally take the $x$- and $y$-image gradients of $\bh_i$ to form differential heightmaps $\bd_{i,x}$ and $\bd_{i,y}$.
The feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\bd_{1,x}, \bd_{1,y}, \bd_{2,x}, \bd_{2,y})$.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.30]{figures/illustrations/local_feature_model.eps}
\caption{Illustration of three local surface heightmaps extracted on a teapot. Each heightmap is ``rendered" along the grasp axis $\bv_i$ at contact $\bc_i$ and oriented by the directions of maximum variation in the heightmap.  We use gradients of the heightmaps for similiarity between grasps in Dex-Net.}
\figlabel{local-feature-model}
\vspace*{-15pt}
\end{figure}

\section{Deep Learning for Object Similarity}
\seclabel{object-similarity}
We use Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi} to efficiently index prior 3D object and grasp data from Dex-Net by embedding each object in a vector space where distance represents object similarity, as shown in \figref{global-feature-model}.
We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and spaced on a grid of angle increments $\delta_{\theta} = \frac{2 \pi}{5}$ and $\delta_{\phi} = \frac{2 \pi}{5}$ on a viewing sphere with radii $r = R, 2R$, where $R$ is the maximum dimension of the object bounding box.
Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
We initialize the weights of the network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4,096 dimensions to 100 dimensions.
This yields the representation $\psi(\mO) \in \mathbb{R}^{100}$ for each object.

Given the MV-CNN object representation, we measure the dissimilarity between two objects $\mO_i$ and $\mO_j$ by the Euclidean distance $\| \psi(\mO_i) - \psi(\mO_j) \|_2$.
For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.
In our implementation, we trained the MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models from the SHREC 2014 dataset ~\cite{li2015comparison}, which has 171 unique categories, for 500,000 iterations of SGD.
%The final PCA step captured approximately 85\% of the variance of the vectors.
%The image classification training step had a test accuracy of 76\%.
To validate the implementation, we tested on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% achieved by the winner of SHREC 2014~\cite{li2015comparison}.

>>>>

\subsection{Grasp Sampling}
\seclabel{grasp-sampling}
Each 3D object $\mO_i$ in Dex-Net is labelled with up to 250 parallel-jaw grasps and their $P_F$.
We generate $K$ grasps for each object using a modification of the 2D algorithm presented in Smith et al.~\cite{smith1999computing} to concentrate samples on grasps that are antipodal~\cite{mahler2015gp}.
To sample a single grasp, we generate a contact point $\bc_1$ by sampling uniformly from the object surface $\mS$, sample a direction $\bv \in \bS^2$ uniformly at random from the friction cone, and find an antipodal contact $\bc_2$ on the line $\bc_1 + t\bv$ where $t \geq 0$.
We add the grasp $\bg_{i,k} = (0.5(\bc_1 + \bc_2), \bv)$ to the candidate set if the contacts are antipodal~\cite{mahler2015gp}.
We evaluated $P_F(\bg_{i,k})$ using Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} by sampling the object pose, gripper pose, and friction random variables $N=500$ times and recording $Z_{i,k}$, the number of samples for which $\bg_{i,k}$ achieved force closure ($F=1$).

@@

\subsection{Grasp Differential Depthmap Features}
\seclabel{grasp-similarity}
To measure grasp similarity, we embed each grasp $\bg = (\bx ,\bv)$ on object $\mO$ in Dex-Net in a feature space based on a 2D map of the  local surface orientation at the contacts, inspired by grasp heightmaps~\cite{herzog2014learning, kappler2015leveraging}.
We generate a depthmap $\bd_{i}$ for contact $\bc_i$ by orthogonally projecting the local object surface onto an $m \times m$ grid centered at $\bc_i$ and oriented along the line to the object center of mass, $\ba_i = \bz - \bc_i$.
Since $F$ only depends on $\bc_i$ and its surface normal, rotations of $\bd_i$ about $\ba_i$ correspond to grasps of the equivalent quality.
We therefore make each $\bd_i$ rotation-invariant by orienting its axes along the eigenvectors of a weighted covariance matrix of the 3D surface points that generate $\bd_i$ as described in~\cite{salti2014shot}.
\figref{local-feature-model} illustrates local surface patches extracted by this procedure.
We finally take the $x$- and $y$-image gradients of $\bd_i$ to form differential depthmaps $\nabla_x \bd_{i}$ and $\nabla_y \bd_{i}$, motivated by the dependence of $F$ on surface normals~\cite{pokorny2013c}, 
The feature vector for each grasp-object pair  in Dex-Net is $\eta(\bg, \mO) = (\nabla_x \bd_{1}, \nabla_y \bd_{1}, \nabla_x \bd_{2}, \nabla_x \bd_{2})$.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.30]{figures/illustrations/local_feature_model.eps}
\caption{Illustration of three local surface depthmaps extracted on a teapot. Each depthmap is ``rendered" along the grasp axis $\bv_i$ at contact $\bc_i$ and oriented by the directions of maximum variation in the depthmap.  We use gradients of the depthmaps for similiarity between grasps in Dex-Net.}
\figlabel{local-feature-model}
\vspace*{-15pt}
\end{figure}

\section{Deep Learning for Object Similarity}
\seclabel{object-similarity}
We use Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi} to efficiently index prior 3D object and grasp data from Dex-Net by embedding each object in a vector space where distance represents object similarity, as shown in \figref{global-feature-model}.
We first render every object on a white background in a total of $N_c = 50$ virtual camera views oriented toward the object center and spaced on a grid of angle increments $\delta_{\theta} = \frac{2 \pi}{5}$ and $\delta_{\phi} = \frac{2 \pi}{5}$ on a viewing sphere with radii $r = R, 2R$, where $R$ is the maximum dimension of the object bounding box.
Then we train a CNN with the architecture of AlexNet~\cite{krizhevsky2012imagenet} to predict the 3D object class label for the rendered images on a training set of models. 
We initialize the weights of the network with the weights learned on ImageNet by Krizhevsky et al.~\cite{krizhevsky2012imagenet} and optimize using Stochastic Gradient Descent (SGD). 
Next, we pass each of the $N_c$ views of each object through the optimized CNN and max-pool the output of the fc7 layer, the highest layer of the network before the class label prediction. 
Finally, we use Principal Component Analysis (PCA) to reduce the max-pooled output from 4,096 dimensions to a 100 dimensional feature vector $\psi(\mO)$.

Given the MV-CNN object representation, we measure the dissimilarity between two objects $\mO_i$ and $\mO_j$ by the Euclidean distance $\| \psi(\mO_i) - \psi(\mO_j) \|_2$.
For efficient lookups of similar objects, Dex-Net contains a KD-Tree nearest neighbor query structure with the feature vectors of all prior objects.
In our implementation, we trained the MV-CNN using the Caffe library~\cite{jia2014caffe} on rendered images from a training set of approximately $6,000$ 3D models sampled from the SHREC 2014~\cite{li2015comparison} portion of Dex-Net, which has 171 unique categories, for 500,000 iterations of SGD.
%The final PCA step captured approximately 85\% of the variance of the vectors.
%The image classification training step had a test accuracy of 76\%.
To validate the implementation, we tested on the SHREC 2014 challenge dataset and achieved a 1-NN accuracy of 86.7\%, compared to 86.8\% achieved by the winner of SHREC 2014~\cite{li2015comparison}.

### 2016-02-05 ICRA2016/bandits_docs/includes/experiments.tex
Made first round of ICRA revisions, v14 of the paper

We evaluate the convergence rate of the Dex-Net 1.0 algorithm for varying sizes of prior data used from Dex-Net and explore the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
We created two training sets of 1,000, and 10,000 objects by uniformly sampling objects from Dex-Net.
We uniformly sampled a set of 300 validation objects for selecting algorithm hyperparameters and selected a set of 45 test objects from the remaining objects.
We ran the algorithm with $N_n = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1.0$~\cite{laskey2015bandits}, and a lower confidence bound containing $p=75\%$ of the belief distribution.
We used isotropic Gaussian uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
For each experiment we compare the Dex-Net algorithm to Thompson sampling without priors (TS) and uniform allocation (UA)~\cite{laskey2015bandits}.

The inverse kernel bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
The inverse bandwidths of the similarity kernel were $C_g = diag(0,0,175, 175)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma_d = 1.75$ for the differential heightmap features, and $C_s = 0.001 * I$ for the shape similarity features.

To scale the experiments, we developed a Cloud-based system on top of Google Cloud Platform.
We used Google Compute Engine (GCE) to distribute trials of MAB algorithms across objects and Google Cloud Storage to store Dex-Net.
The system launched up to 1,500 GCE virtual instances at once for experiments, reducing the runtime by three orders of magnitude.
Each virtual instance ran Ubuntu 12.04 on a single core with 3.75 GB of RAM.

\subsection{Scaling of Average Convergence Rate}
\seclabel{conv-rate}
To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran the Dex-Net 1.0 algorithm on the test objects with priors computed from 1,000 and 10,000 objects from Dex-Net. 
~\figref{avg-reward} shows the normalized $P_F$  (the ratio of the $P_F$ for the sampled grasp to the highest $P_F$ of the 250 candidate grasps) versus iteration averaged over 25 trials for each of the test objects over 2,000 iterations.
The average runtime per iteration was 16 ms for UA, 17 ms for TS, and 22 ms for Dex-Net 1.0.
The algorithm with 10,000 objects takes approximately 2$\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by TS.
Furthermore, the 10,000 object curve does not fall below approximately 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.41]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
\caption{Failure object for the Dex-Net 1.0 algorithm. (Top) The drill, which is relatively rare in the dataset, has no geometrically similar neighbors even with 10,000 objects. (Bottom) Plotted is the average normalized grasp quality versus iteration over 25 trials for the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior 3D objects. The lack of similar objects leads to no significant performance increase over Thompson sampling without priors. }
\figlabel{avg-reward-drill}
\vspace*{-10pt}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.21]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the normalized grasp quality versus iteration averaged over 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects.
%with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
(Top-left) Using a higher inverse bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
(Top-right) A lower inverse bandwith decreases the convergence rate, but on average the Dex-Net Algorithm still selects a grasp within approximately 85\% of the grasp with highest $P_F$ for all iterations.
(Bottom-left) Lower uncertainty increases the quality for all methods, (bottom-right) higher uncertainty decreases the quality for all methods, and the Dex-Net algorithm with 10,000 prior objects still converges approximately 2$\times$ faster than Thompson sampling without priors. 
}
\figlabel{bnu-sens}
\vspace*{-15pt}
\end{figure}

>>>>

We evaluate the convergence rate of the Dex-Net 1.0 algorithm using force closure as our binary quality metric for varying sizes of prior data used from Dex-Net, and we explore the sensitivity of the convergence rate to object shape, the similarity kernel bandwidths, and uncertainty.
We created two training sets of 1,000, and 10,000 objects by uniformly sampling objects from Dex-Net.
We uniformly sampled a set of 300 validation objects for selecting algorithm hyperparameters and selected a set of 45 test objects from the remaining objects.
We ran the algorithm with $M = 10$ nearest neighbors, $\alpha_0 = \beta_0 = 1$~\cite{laskey2015bandits}, and a lower confidence bound containing $q=75\%$ of the belief distribution.
We used isotropic Gaussian uncertainty with object and gripper translation variance $\sigma_{t} = 0.005$, object and gripper rotation variance $\sigma_{r} = 0.1$, and friction variance $\sigma_{\gamma} = 0.1$.
For each experiment we compare the Dex-Net algorithm to Thompson sampling without priors (TS)~\cite{laskey2015bandits}, a state-of-the-art method for robust grasp planning, and uniform allocation (UA), a widely-used method for robust grasp planning the selects the next grasp to evaluate uniformly at random~\cite{kehoe2012toward, kim2012physically, weisz2012pose}.

The inverse kernel bandwidths were selected by maximizing the log-likelihood of the true $P_F$ under the CCBP model~\cite{goetschalckx2011continuous} on the validation set using a grid search over hyperparameters.
The inverse bandwidths of the similarity kernel were $C_g = diag(0,0,3e-5, 3e-5)$ for the grasp parameter features, an isotropic Gaussian mask $C_d$ with mean $\mu_d = 500.0$ and $\sigma_d = 0.33$ for the differential heightmap features, and $C_s = 1e6 * I$ for the shape similarity features.

To scale experiments, we developed a Cloud-based system on top of Google Cloud Platform.
We used Google Compute Engine (GCE) to construct the Dex-Net 1.0 dataset and to distribute subsets of objects to virtual machines for MAB experiments, and we used Google Cloud Storage to store Dex-Net.
The system launched up to 1,500 GCE virtual instances at once for experiments, reducing the runtime by an estimated three orders of magnitude to approximately 315 seconds per object.
Each virtual instance ran Ubuntu 12.04 on a single core with 3.75 GB of RAM.

\subsection{Scaling of Average Convergence Rate}
\seclabel{conv-rate}
To examine the effects of orders of magnitude of prior data on convergence to a grasp with high $P_F$, we ran the Dex-Net 1.0 algorithm on the test objects with priors computed from 1,000 and 10,000 objects from Dex-Net. 
~\figref{avg-reward} shows the normalized $P_F$  (the ratio of the $P_F$ for the best grasp predicted by the algorithm on iteration $t$ to the highest $P_F$ of the candidate grasps) versus iteration averaged over 25 trials for each of the test objects over 2,000 iterations.
The average runtime per iteration was 16 ms for UA, 17 ms for TS, and 22 ms for Dex-Net 1.0.
The algorithm with 10,000 objects takes approximately 2$\times$ fewer iterations to reach the maximum normalized $P_F$ value reached by TS.
Furthermore, the 10,000 object curve does not fall below approximately 90\% of the best grasp in the set across all iterations, suggesting that a grasp with high $P_F$ is found using prior data alone.
This speedup is promising for binary success metrics that are expensive to  evaluate, such as human labels or physical grasping trials.

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.39]{figures/illustrations/drill_avg_reward_w_neighbors.eps}
\caption{Failure object for the Dex-Net 1.0 algorithm. (Top) The drill, which is relatively rare in the dataset, has no geometrically similar neighbors even with 10,000 objects. (Bottom) Plotted is the average normalized grasp quality versus iteration over 25 trials for the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior 3D objects. The lack of similar objects leads to no significant performance increase over Thompson sampling without priors. }
\figlabel{avg-reward-drill}
\vspace*{-10pt}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.21]{figures/illustrations/combined_weight_and_u_sensitivity.eps}
\caption{Sensitivity to similiarity kernel (top) and pose and friction uncertainty (bottom) for the normalized grasp quality versus iteration averaged over 25 trials per object for the Dex-Net algorithm with 1,000 and 10,000 prior 3D objects.
%with a higher heightmap gradient kernel bandwidth of $1 / 350$ (left) and a lower kernel bandwidth of $1 / 450$ (right).
(Top-left) Using a higher inverse bandwidth causes the algorithm to measure false similarities between grasps, leading to performance on par with uniform allocation.
(Top-right) A lower inverse bandwith decreases the convergence rate, but on average the Dex-Net algorithm still selects a grasp within approximately 85\% of the grasp with highest $P_F$ for all iterations.
(Bottom-left) Lower uncertainty increases the quality for all methods, (bottom-right) higher uncertainty decreases the quality for all methods, and the Dex-Net algorithm with 10,000 prior objects still converges approximately 2$\times$ faster than Thompson sampling without priors. 
}
\figlabel{bnu-sens}
\vspace*{-15pt}
\end{figure}

### 2016-02-05 ICRA2016/bandits_docs/includes/introduction.tex
Made first round of ICRA revisions, v14 of the paper

Cloud-based Robotics and Automation systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
Potential advantages to using the Cloud include Big Data: access to updated libraries of images, maps, and object/product data; and Parallel Computation: access to parallel grid computing for statistical analysis, machine learning, and planning~\cite{kehoe2015survey}.
These benefits have recently been demonstrated in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of research on analytic methods.
This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, and environment configurations~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.45]{figures/illustrations/spray_bottle_avg_reward_w_neighbors.eps}
\caption{Normalized grasp quality versus iteration averaged over 25 trials for the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle. We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation. (Top) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set. (Bottom) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp with 10,000 prior objects.}
\figlabel{avg-reward-spray}
\vspace*{-20pt}
\end{figure}
The primary contribution of this paper is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
The algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.

To study scaling effects, we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 unique 3D object models selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
To the best of our knowledge, this is the largest object dataset used for grasping research to-date.
We also incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.

We implement the algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
Experiments suggest that using 10,000 prior object models from Dex-Net reduces the number of samples needed to plan robust parallel-jaw grasps by up to 2$\times$ on average over 45 objects.
%\TODO{Update with final results}

>>>>

Cloud-based Robotics and Automation systems exchange data and perform computation via networks instead of operating in isolation with limited computation and memory.
Potential advantages to using the Cloud include Big Data: access to updated libraries of images, maps, and object/product data; and Parallel Computation: access to parallel grid computing for statistical analysis, machine learning, and planning~\cite{kehoe2015survey}.
These benefits have recently been demonstrated in vision and speech, where datasets with millions of examples such as ImageNet have produced results~\cite{hannun2014deepspeech, krizhevsky2012imagenet} that surpass those obtained from decades of previous research.
This suggests that large-scale machine learning of grasps for vast numbers of possible object shapes, object poses, and environment configurations~\cite{goldfeder2011data, lenz2015deep, kappler2015leveraging}, could exhibit scaling effects similar to those observed in computer vision and speech recognition.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.45]{figures/illustrations/spray_bottle_avg_reward_w_neighbors.eps}
\caption{Average normalized grasp quality versus iteration for 25 trials for the Dex-Net1.0 algorithm with 1,000 and 10,000 prior 3D objects from Dex-Net (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle. We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors~\cite{laskey2015bandits} and uniform allocation~\cite{kehoe2012toward, weisz2012pose}. (Top) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set. (Bottom) As a result, the Dex-Net 1.0 algorithm quickly converges to the optimal grasp with 10,000 prior objects.}
\figlabel{avg-reward-spray}
\vspace*{-20pt}
\end{figure}

The primary contribution of this paper is the Dex-Net 1.0 algorithm for quickly finding a grasp with high probability of success for a binary grasp quality metric under uncertainty based on Multi-Armed Bandits (MABs).
The algorithm speeds up robust grasp planning by learning from a large dataset of prior grasps and 3D object models using Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a distribution on the quality of each grasp from prior data.

To study scaling effects, we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 unique 3D object models selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
To the best of our knowledge, this is the largest object dataset used for grasping research to-date.
We incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects for predicting robust grasp quality with CCBPs.

We implement the Dex-Net 1.0 algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
Experiments suggest that using 10,000 prior object models from Dex-Net reduces the number of samples needed to plan parallel-jaw grasps by up to 2$\times$ on average over 45 objects using the probability of force closure as a success metric.
%\TODO{Update with final results}
